Concurrent Programming with CXL

### 2020-06-23 book/paper.tex
Starting to add more non-blocking examples
Added something about the alloc module

@@

@@

\vspace{1em}
\begin{tabular}{|l|l|}
\hline
\texttt{subseq(t, b, f)} & return a \emph{slice} of list \texttt{t} starting
at index \texttt{b} and ending just before index \texttt{f}\\
\hline
\texttt{append(t, e)} & append \texttt{e} to list \texttt{t}\\
\hline
\texttt{head(t)} & return the first element of list \texttt{t}\\
\hline
\texttt{tail(t)} & return all but the first element of list \texttt{t}\\
\hline
\texttt{qsort(t)} & sort list \texttt{t} using quicksort\\
\hline
\texttt{list2bag(t)} & convert list \texttt{t} into a bag \\
\hline
\texttt{list2set(t)} & convert list \texttt{t} into a set \\
\hline
\texttt{listMin(t)} & return the minimum of all elements in \texttt{t}\\
\hline
\texttt{listMax(t)} & return the maximum of all elements in \texttt{t}\\
\hline
\texttt{listSum(t)} & return the sum of all elements in \texttt{t}\\
\hline
\end{tabular}

>>>>

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{code/lst1.cxl}
\end{code}
\caption{[lst1.cxl] List with non-blocking read operations, part 1.}
\label{fig:lst1}
\end{figure}

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{code/lst2.cxl}
\end{code}
\caption{[lst2.cxl] List with non-blocking read operations, part 2.}
\label{fig:lst2}
\end{figure}

@@

The \texttt{alloc} module
\index{alloc module}
support thread-safe dynamic allocation of ``records.''
Each record has two fields: \texttt{.data} and \texttt{.next} that
can be used arbitrarily, although \texttt{.next} is intended to be
used as a pointer to another record.
There are just two methods:

\vspace{1em}
\begin{tabular}{|l|l|}
\hline
\texttt{rec\_alloc()} & allocate a record \\
\hline
\texttt{rec\_free(r)} & free record \texttt{r} \\
\hline
\end{tabular}
\vspace{1em}

CXL supports an address value \texttt{NULL} that can be
used as a null pointer.  \texttt{rec\_alloc} returns \texttt{NULL}
when running out of memory.

@@

\vspace{1em}
\begin{tabular}{|l|l|}
\hline
\texttt{subseq(t, b, f)} & return a \emph{slice} of list \texttt{t} starting
at index \texttt{b} and ending just before index \texttt{f}\\
\hline
\texttt{append(t, e)} & append \texttt{e} to list \texttt{t}\\
\hline
\texttt{head(t)} & return the first element of list \texttt{t}\\
\hline
\texttt{tail(t)} & return all but the first element of list \texttt{t}\\
\hline
\texttt{listQsort(t)} & sort list \texttt{t} using quicksort\\
\hline
\texttt{list2bag(t)} & convert list \texttt{t} into a bag \\
\hline
\texttt{list2set(t)} & convert list \texttt{t} into a set \\
\hline
\texttt{listMin(t)} & return the minimum of all elements in \texttt{t}\\
\hline
\texttt{listMax(t)} & return the maximum of all elements in \texttt{t}\\
\hline
\texttt{listSum(t)} & return the sum of all elements in \texttt{t}\\
\hline
\end{tabular}
